ICM testing

### 2023-03-17 Scripts/ASR_stocks.Rmd
Mostly a tuning script update
Have the 'tuning' simulations working, this backup will include some initial testing of that.

```{r, echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)

@@

# summary plots for ALL stocks
for (i in unique(ASR_long$Stock)) {
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)
  maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
  maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
  minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
  forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
  forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
  p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
        geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
        theme_bw() + 
        ggtitle(i) +
    guides(x =  guide_axis(angle = 90)) 
  print(p1)

  if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))

  png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
  print(p1)
  dev.off()
}

@@

# Stocks <- ASR_stocks %>%
#                       dplyr::group_by(Stock, Species, type) %>%
#                       dplyr::summarize(ages=length(unique(age)),
#                                 years=length(unique(Year))) %>%
#                       dplyr::arrange(-years, -ages) %>%
#                       dplyr::filter(!Species=="morhua") %>%
#                       dplyr::distinct(Stock) %>%
#                       dplyr::pull(Stock)
# 
# print(Stocks)
Stocks <- Stocks$Stock
# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly modle.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
# Bring in the data
# Handy import function from the rio package... tricky part was getting the right filename here...
for(i in Stocks){
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

@@

  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data %>% dplyr::pull(Year) %>% unique() %>% sort()
  N.end <- sum(data[data$Year==max(years),]$Num)
  #N.end <- rowSums(abund[nrow(abund),-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  #vpa.abund <- rowSums(abund[,-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num)) %>% pull(vpa)

@@

  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
  # For the years of mx without SSB info to inform them
  if(minage >0 ) 
  {
    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
    names(mx) <- names(mx.fill)
   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  }
  source("D:/Github/ICM/Scripts/functions/backwards_sim.R")

  tst <- icm.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = minage:maxage,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 5,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

@@

  # All the results in a plot
  p2 <- ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i) +
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # Same thing but functional boxplots
  p3 <- ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + #geom_vline()
          ggtitle(i)+
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  p4 <- ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Lotka r") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i)

  #print(p2)
  #print(p3)
  #print(p4)

  png(filename=paste0("D:/Github/ICM/Figures/", i, "/runs_vs_vpa_", i, ".png"), height=4, width=6, res=400, units="in")
  print(p2)
  dev.off()
  png(filename=paste0("D:/Github/ICM/Figures/", i, "/runs_vs_vpa_ribbon_", i, ".png"), height=4, width=6, res=400, units="in")
  print(p3)
  dev.off()
  png(filename=paste0("D:/Github/ICM/Figures/", i, "/growth_", i, ".png"), height=4, width=6, res=400, units="in")
  print(p4)
  dev.off()
}
```

>>>>

```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)

@@

# summary plots for ALL stocks, this is already run, so lets not keep running it
# for (i in unique(ASR_long$Stock)) {
#   ASR_sub <- ASR_long %>%
#     dplyr::select(Year, Stock, type, age, value) %>%
#     dplyr::filter(Stock==i)
#   maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]),na.rm=T)
#   maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
#   minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)],na.rm=T)
#   forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
#   forplot <- forplot[!is.na(forplot$value),] # remove the NAs, hopefully this works for all the stocks...
#   p1 <- ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
#         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
#         theme_bw() + 
#         ggtitle(i) +
#     guides(x =  guide_axis(angle = 90)) 
#   print(p1)
#   
#   if(!dir.exists(paste0("D:/Github/ICM/Figures/", i))) dir.create(paste0("D:/Github/ICM/Figures/", i))
#   
#   png(filename=paste0("D:/Github/ICM/Figures/", i, "/data_summary_", i, ".png"), height=4, width=12, res=400, units="in")
#   print(p1)
#   dev.off()
# }

@@

# Stocks <- ASR_stocks %>%
#                       dplyr::group_by(Stock, Species, type) %>%
#                       dplyr::summarize(ages=length(unique(age)),
#                                 years=length(unique(Year))) %>%
#                       dplyr::arrange(-years, -ages) %>%
#                       dplyr::filter(!Species=="morhua") %>%
#                       dplyr::distinct(Stock) %>%
#                       dplyr::pull(Stock)
# 
# print(Stocks)
Stocks <- Stocks$Stock
# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly modle.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]

back.res <- NULL
back.ts <- NULL
back.ts.quants <- NULL
tuned.res <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

@@

  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data %>% dplyr::pull(Year) %>% unique() %>% sort()

  N.end <- sum(data[data$Year==max(years),]$Num)
  #N.end <- rowSums(abund[nrow(abund),-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  #vpa.abund <- rowSums(abund[,-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num)) %>% pull(vpa)

@@

  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()

  # Dealing with some annoying NAs...
  if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
  {
    age.mat[length(years),] <- age.mat[length(years)-1,]
    prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
    weight.age[length(years),] <- weight.age[length(years)-1,]
    mx[length(years),13:23] <- mx[length(years),12]
  }

  if(i == "DFO_2J3KL_Gadus_morhua")
  {
    age.mat[,8:10] <- 1
    prop.nat.mort[,8:10] <- prop.nat.mort[,7]
    weight.age[12:14,9:10] <- weight.age[12:14,8]
    weight.age[15,10] <- weight.age[15,9]
    mx[12:16,9:10] <- mx[12:16,8]
    mx[17,10] <- mx[17,9]
  }

  if(i == "DFO_4T-Spring_Clupea_harengus")
  {
    age.mat[6:7,10] <- 1
    prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
    weight.age[6:7,10] <- weight.age[6:7,9]
    mx[6:9,10] <- mx[6:9,9]
  }

  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
  {
    age.mat[30,8] <- 1
    prop.nat.mort[30,8] <- prop.nat.mort[30,7]
    weight.age[30,8] <- weight.age[29,8]
    mx[30:31,8] <- mx[30:31,9]
  }

  if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
  {
    age.mat[c(14,27,40),5] <- age.mat[1,5]
    prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
    weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
    mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
  }

  # For the years of mx without SSB info to inform them
  if(minage >0 ) 
  {
    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
    names(mx) <- names(mx.fill)
   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  }

  tst <- icm.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = minage:maxage,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 500,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

  back.res[[i]] <- tst
  back.ts[[i]] <- did.it.work
  back.ts.quants[[i]] <- quants

@@

  # All the results in a plot
  p2 <- ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i) +
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
  # Same thing but functional boxplots
  p3 <- ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + #geom_vline()
          ggtitle(i)+
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_ribbon_", i, ".png"), base_width = 6,base_height = 4)

  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  p4 <- ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Lotka r") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i)
  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/lokta_r_", i, ".png"), base_width = 6,base_height = 4)

# Now run the tuning sims

  nm = prop.nat.mort

  source("D:/Github/ICM/Scripts/functions/tuning_sim.R")
  N.end <- vpa.abund[length(vpa.abund)]
  tunes <- tune.sim(years,
                    n.steps = 100,
                    abund.ts = vpa.abund,
                    mat.age = age.mat,
                    nm = prop.nat.mort,
                    w.age = weight.age,
                    ages = minage:maxage,
                    rems = rem$rem,
                    fecund = mx,
                    N.end = N.end,
                    pop.model = 'exponential')

  tuned.res[[i]] <- tunes

  # Comparing our new time series with the old
  p2 <- ggplot() +
          geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
          geom_line(data=tunes$res, aes(x=year,y=vpa.n),color='black') +
          xlab("") +
          ylab("Abundance (1000s)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/tunded_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)

  # Comparing the absolute miss from the tuned time series
   p3 <- ggplot() +
          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.n),color='red') +
          xlab("") +
          ylab("Difference in abundance (1000s)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) 
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_N_", i, ".png"), base_width = 6,base_height = 4)

  # What percentage (mean) difference
   p4 <- ggplot() +
          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
          xlab("") +
          ylab("Difference in abundance (%)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_N_", i, ".png"), base_width = 6,base_height = 4)

     # Difference in m's
   p5 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.m),color='red') +
          xlab("") +
          ylab("Difference in natural mortality (Proportional)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p5, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_m_", i, ".png"), base_width = 6,base_height = 4)
     # % Difference in m's
   p6 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
          xlab("") +
          ylab("Difference in natural mortality (%)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)

   p7 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=mn.m),color='blue') +
          geom_line(data=tunes$res[-1,], aes(x=year,y=vpa.m),color='black') +
          xlab("") +
          ylab("Natural mortality (Proportional)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p7, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Nat_M_", i, ".png"), base_width = 6,base_height = 4)

     p8 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=r),color='blue') +
          xlab("") +
          ylab("Lotka r") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p8, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Lotka_r_", i, ".png"), base_width = 6,base_height = 4)

}
saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
```

```{r, forward-sims-n-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
```
